SAT Competition 2020\tnoteref{title}

### 2021-01-11 paper/main.tex

@@

>>>>

\definecolor{redorange}{rgb}{0.878431, 0.235294, 0.192157}
\definecolor{lightblue}{rgb}{0.552941, 0.72549, 0.792157}
\definecolor{clearyellow}{rgb}{0.964706, 0.745098, 0}
\definecolor{clearorange}{rgb}{0.917647, 0.462745, 0}
\definecolor{mildgray}{rgb}{0.54902, 0.509804, 0.47451}
\definecolor{softblue}{rgb}{0.643137, 0.858824, 0.909804}
\definecolor{bluegray}{rgb}{0.141176, 0.313725, 0.603922}
\definecolor{lightgreen}{rgb}{0.709804, 0.741176, 0}
\definecolor{redpurple}{rgb}{0.835294, 0, 0.196078}
\definecolor{midblue}{rgb}{0, 0.592157, 0.662745}
\definecolor{clearpurple}{rgb}{0.67451, 0.0784314, 0.352941}
\definecolor{browngreen}{rgb}{0.333333, 0.313725, 0.145098}
\definecolor{darkestpurple}{rgb}{0.396078, 0.113725, 0.196078}
\definecolor{greypurple}{rgb}{0.294118, 0.219608, 0.298039}
\definecolor{darktruqoise}{rgb}{0, 0.239216, 0.298039}
\definecolor{darkbrown}{rgb}{0.305882, 0.211765, 0.160784}
\definecolor{midgreen}{rgb}{0.560784, 0.6, 0.243137}
\definecolor{darkred}{rgb}{0.576471, 0.152941, 0.172549}
\definecolor{darkpurple}{rgb}{0.313725, 0.027451, 0.470588}
\definecolor{darkestblue}{rgb}{0, 0.156863, 0.333333}
\definecolor{lightpurple}{rgb}{0.776471, 0.690196, 0.737255}
\definecolor{softgreen}{rgb}{0.733333, 0.772549, 0.572549}
\definecolor{offwhite}{rgb}{0.839216, 0.823529, 0.768627}

@@

\subsection{Best Tuples and Triples}

When selecting solvers for instance-specific algorithm selection, it is interesting to know about the complementarity of the performance of solvers. 
We created analyzed all pairs and triples of submitted solvers and calculated the PAR-2 score of the VBS of the resulting set of solvers.

\begin{table}
\centering
\begin{tabular}{|l|l|l|}
\hline
Solver 1 & Solver 2 & VBS score \\
\hline
\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \\
\solver{Kissat} & \solver{CryptoMiniSat-CCAnr} & \\
\solver{Kissat} & \solver{CryptoMiniSat-CCAnr} & \\
\solver{Kissat unsat} & \solver{CryptoMiniSat-CCAnr LSIDS} & \\
\solver{Kissat} & \solver{Relaxed Maple newTech} & \\
\hline
\end{tabular}
\end{table}

\begin{table}
\begin{tabular}{|l|l|l|l|}
\hline
Solver 1 & Solver 2 & Solver 3 & VBS score \\
\hline
\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{CryptoMiniSat-Walksat} & \\
\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{MapleCOMSPS\_LRB\_VSIDS\_2 init} &  \\
\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{CryptoMiniSat-CCAnr} & \\
\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{cadical\_alluip\_trail} & \\
\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{cadical\_alluip} & \\
\hline
\end{tabular}
\end{table}
